%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{psyqe-resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shaunak}{Guha}{ 
\urlstyle{same}
\faIcon{laptop-code} \ Research Scientist \ 
\ \faIcon[regular]{calendar-alt} \ 24 years
\\
%\href{https://www.linkedin.com/in/shaunakguha/}{ LinkedIn/shaunakguha } \ | \

\faIcon[regular]{envelope} \href{mailto:mr.shaunakguha@gmail.com}{ mr.shaunakguha@gmail.com } \ 
\faIcon{map-marker-alt} \ Kolkata, India

}
\vspace{1pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.34\textwidth} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
%Facebook:// \href{https://facebook/dd}{\bf dd} \\
\faIcon{linkedin} \ LinkedIn://\href{https://www.linkedin.com/in/shaunakguha}{\bf shaunakguha} \\
\faIcon{researchgate} \ ResearchGate://\href{https://www.researchgate.net/profile/Shaunak-Guha}{\bf Shaunak-Guha} \\
\faIcon{github} \ Github://\href{https://github.com/psyqe}{\bf psyqe} \\
%YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\
%Twitter://  \href{https://twitter.com/debarghya_das}{\bf @debarghya\_das} \\
%Quora://  \href{https://www.quora.com/Debarghya-Das}{\bf Debarghya-Das}
\vspace{-3pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{M.Sc. in Physics}
\descript{St. Xavier's College, Kolkata}
University of Calcutta \\
\location{Division : First Class} 
\location{Nov 2020 | CGPA : 7.42 / 10}
\vspace{4pt}
\sectionsep

%\subsection{B.Sc. in Physics\fontspec[Path = fonts/raleway/]{Raleway-Medium} \fontsize{13pt}{14pt} \selectfont{( Honours )}}
\subsection{B.Sc. in Physics \sffamily{( Honours )}}
\descript{St. Xavier's College, Kolkata}
University of Calcutta \\
\location{Division : First Class}
\location{ July 2018 | CGPA : 6.79 / 10}
\vspace{4pt}
\sectionsep

\subsection{ISC (Class 12)}
\descript{St. Joseph's College, Kolkata}
Council for the Indian School Certificate Examinations \\
\location{June 2015 |  Score : 95.75 \%}
\vspace{4pt}
\sectionsep

\subsection{ICSE (Class 10)}
\descript{St. Joseph's College, Kolkata}
Council for the Indian School Certificate Examinations \\
\location{June 2013 |  Score : 91.4 \%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
%\subsection{Programming}
\location{Programming}
\vspace{1pt}
\textbullet{} Java \textbullet{} Python \textbullet{} C++ \textbullet{}
Assembly \textbullet{} \\
\textbullet{} Matlab \textbullet{} SQL \textbullet{} \LaTeX\ \textbullet{} Bash/Shell \textbullet{} \\
\vspace{4pt}
\location{Soft Skills}
\vspace{1pt}
\textbullet{} Fast learner \textbullet{} Organized workflow \textbullet{} \\
\textbullet{} Open minded \textbullet{} Adaptive \textbullet{} Curious \textbullet{} \\
\vspace{4pt}
\location{Disciplines}
\vspace{1pt}
\textbullet{} Nanotechnology \textbullet{} Electronics \textbullet{} \\
\textbullet{} Solid state physics \textbullet{} Analytics \textbullet{} \\
\vspace{4pt}
\location{Languages}
\begin{tabular}{llc}
\vspace{-8pt} \\
\textbullet{} \textbf{English} & - & 4.5 / 5 \\
\textbullet{} \textbf{Bengali} & - & 4.5 / 5 \\
\textbullet{} \textbf{Hindi} & - & 4.0 / 5 \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Prophecy Sensorlytics}
\descript{| \ Research Scientist }
\location{December 2021 – Present \  | \ Kolkata, India \ | \ 8 months}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Interdisciplinary and collaborative R\&D on sensor design using materials  engineering, circuit modelling, data science \&  UI/UX of final product
\item A typical work week includes sensor prototyping, characterisation, device testing \& improvisation, data analysis, firmware \& middleware revision, up-scaling for fabrication, production planning and project management 
\end{tightemize}
\sectionsep

\runsubsection{Chegg Inc.}
\descript{\hspace{-2pt}| \ Advanced Physics Expert }
\location{March 2021 – Present \ | \ Part-time }
\begin{tightemize}
\item Solved problems \& doubts on topics from high-school and undergraduate physics, mathematics and computer science.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research \& Projects}
\runsubsection{Indian Association for the Cultivation of Science \\ ( IACS, Kolkata )}
\descript{| \ Research Consultant}
\location{February 2021 - August 2021 \ | \ Kolkata, India}
\begin{tightemize}
\item  Designed and programmed a stable and configurable DC supply tool for characterisation and routine testing of solid-state electrochromic device prototypes in the lab of \textbf{\href{http://iacs.res.in/faculty-profile.html?id=112}{Prof. Subhadeep Datta}} and \textbf{\href{http://iacs.res.in/faculty-profile.html?id=68}{Prof. Sudip Malik}}
\end{tightemize}
\sectionsep


\runsubsection{St. Xavier's College, Kolkata}
\descript{| \ Master's Dissertation}
\location{July 2019 - March 2020 \ | \ Kolkata, India}
\begin{tightemize}
\item Fabricated CZTS thin films using SILAR for use as thin film solar cells and studied their active surface using SEM-EDX to analyze ion adsorption \cite{Guha2021}
\end{tightemize}
\sectionsep

\runsubsection{Indian Institute of Technology (IIT), Bombay}
\descript{| \ Internship}
\location{June 2019 \ | \ Mumbai, India}
\begin{tightemize}
\item Participated in FOSSEE (Free/Libre Open Source Software for Education) Summer Fellowship 2019 in the Arduino domain
\item Created a 2-player pingpong game that can be played on a 16x2 LCD
\item Published an online simulation on Autodesk TinkerCAD \textbf{\href{https://www.tinkercad.com/things/cL2SogHJobn?sharecode=Nf75LAH15eyD5xEGsSbnSdjyj0kpy9A-UC08TDohg8E}{[Link]}}
\end{tightemize}
\sectionsep

\runsubsection{St. Xavier's College, Kolkata}
\descript{| \ Bachelor's Dissertation}
\location{October 2017 - April 2018 \ | \ Kolkata , India}
\begin{tightemize}
\item Using motion tracking, studied the movement of a levitating oscillator to estimate parameters of a hypothetical empirical formula using curve fitting
\end{tightemize}
\sectionsep

\runsubsection{Ramakrishna Mission Vivekananda Educational and Research Institute \ ( RKMVERI )} 
\descript{| \ Research Consultant}
\location{2017 - 2018 \ | \ Howrah, India}
\begin{tightemize}
\item Developed a room-wide Arduino-controlled training setup that trains and tracks progress of directional auditory perception of visually impaired people \cite{Prasad2019}. Successful trials in local schools for blind children.
\item IP accepted \textbf{\href{https://search.ipindia.gov.in/DesignApplicationStatus}{(Design No.: 305795)}} and published in the Official Journal of the Patent Office, Govt. of India \textbf{\href{https://search.ipindia.gov.in/IPOJournal/Journal/Patent}{(Journal No.: 27/2019, Pg. 28999)}} \cite{Design2019}
\end{tightemize}
\sectionsep


\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     PAGE TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%\end{tabular}
%\sectionsep

\section{Tests}
\begin{tabular}{rll}
%    2022 & \textbf{GRE} & Score : 320 \\
%    2022 & \textbf{TOEFL} & Score : 100 \\
%    2022 & \textbf{IELTS} & Score : 8.5 \\
    2021 & \textbf{GATE} (Physics) & Rank : 2050 \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFEREES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Referees}

\location{\textcolor{primary}{Dr. Kallol Mohanta}}
Senior Research Scientist \& Team Lead \\
\faIcon{university} \ Prophecy Sensorlytics Pvt Ltd \\
\faIcon[regular]{envelope} \ 
\href{mailto:kmohanta@gmail.com}{\textit{kmohanta@gmail.com}}

\sectionsep

\location{\textcolor{primary}{Prof. Gayatri Banerjee}}
Assitant Professor \\
\faIcon{university} \ St. Xavier's College, Kolkata \\
\faIcon[regular]{envelope}  \  \href{mailto:gayatri_banerjee@sxccal.edu}{\textit{gayatri\_banerjee@sxccal.edu}}

\sectionsep

\location{\textcolor{primary}{Prof. Aditi Ghosh}}
Assistant Professor \\
\faIcon{university} \ St. Xavier's College, Kolkata \\
\faIcon[regular]{envelope} \ 
\href{mailto:aditi@sxccal.edu}{\textit{aditi@sxccal.edu}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications \& Patents} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{is-abbrv}
\bibliography{publications}
\nocite{*}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Solid State Electronics, 
Nanomaterials, Quantum Physics, 
VLSI, Digital Signal Processing, $\mu$c-$\mu$p Architecture, Open Source Computing, Group Theory, Optoelectronics, Communication Theory, Computational Physics  | \href{https://www.sxccal.edu/wp-content/uploads/2019/12/MSc-PhysicsSyllabus2014.pdf}{\bfseries Course Link}
\sectionsep

\subsection{Undergraduate}
Statistical \& Quantum Mechanics, Non-linear Dynamics, Chaos Theory, Electrostatics \& Electrodynamics, Electrical Circuits, RDBMS,  | \href{https://www.sxccal.edu/wp-content/uploads/2020/01/BscPhysicsHonsSyllabus.pdf}{\bfseries Course Link}

\end{minipage}
\end{document}  \documentclass[]{article}
